Risk Perceptions for Wearable Devices

### 2015-03-06 tex-inputs/appendixes.tex
coding labels formatting

\section{Coding Label Definitions}
\label{sec:coding}

Privacy: ``privacy,'' revealing personal information, spying. \\
Security:  ``security,'' compromise, malware, hacking. \\
GPS tracking: ``location,'' ``GPS,'' being monitored.

Unaware use: using data without permission or in a different way than understood by user. \\
Unaware collection: collecting data without permission. \\
Unaware access: disclosure of data without permission. \\
False information: inaccurate or maliciously false data.

Health Risk: radiation, cancer, or long-term effects.\\
Safety: distractions causing car crashes or injuries, mugging or violence because of the device, injuries from device malfunctions (battery burns).\\
Discomfort: eye strain, headache, obscured vision, irritation. \\
Financial cost: getting ripped off by buying the device or device accessories, having to buy another device when broken or stolen, financial compromise caused by device. \\
Theft: the device getting stolen.

Social Impact: dependency, distance from friends and family, changes in decision making, social changes, etc. \\
Social Stigma: judgment, hate, or bystander discomfort.\\ 
Aesthetics: fashion, the device being ugly, mentions of not looking cool/dorky.

Miscellaneous: odd comments, uncommon concerns. \\
None: ``None,'' no threat, perceiving no big concerns \\
Don't know: ``do not know,'' hinting at confusion \\
Don't care: `` do not care,'' nonchalant answers

>>>>

\section{Coding Label Definitions}
\label{sec:coding}
Researchers coded the self reported answers in the following way.\\

{\bf Privacy}: ``privacy,'' mention of personal details, spying. \\
{\bf Security}:  ``security,'' mention of malware, hacking. \\
{\bf GPS tracking}: ``location,'' ``GPS,'' mention of monitoring. \\
{\bf Being Unaware}: mention of using, collecting, and disclosing data without permission or in a different way than understood by user. \\
{\bf False information}: inaccurate or maliciously false data.\\
{\bf Health Risk}: mention of radiation, cancer, or health effects.\\
{\bf Safety}: mention of distractions causing car crashes or injuries, mugging or violence because of the device, injuries from device malfunctions (battery burns).\\
{\bf Discomfort}: mention of eye strain, headache, obscured vision, irritation. \\
{\bf Financial cost}: mention of getting ripped off by buying the device or device accessories, having to buy another device when broken or stolen, financial compromise caused by device. \\
{\bf Theft}: mention of device theft. \\
{\bf Social Impact}: mention of dependency, distance from friends and family, changes in decision making, social changes, etc. \\
{\bf Social Stigma}: mention of judgment, hate, or bystanders.\\ 
{\bf Aesthetics}: mention of fashion, the device being ugly, looking dorky. \\
{\bf Miscellaneous}: odd comments, uncommon concerns. \\
{\bf None}: ``None,'' mention of no threat, or no real concerns \\
{\bf Don't know}: ``do not know,'' general confusion \\
{\bf Don't care}: `` do not care,'' nonchalant answers
